Evolution of pre-copulatory and post-copulatory inbreeding behaviour: a computational approach

### 2016-09-15 ms_pre_post.Rmd
Fix error about magnitude of inbreeding avoidance -- allele versus phenotype value

Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of inbreeding fertilisation strategy facilitates selection for polyandry, shows evolution of tendency for polyandry and inbreeding mating strategy when inbreeding fertilisation strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle. In all cost combinations of Figure 2 (panels A-D), tendency for polyandry allele values decreased over generations, reflecting evolution of monandry. However, values of inbreeding mating strategy alleles did not greatly differ over generations when inbreeding fertilisation strategy was fixed, meaning that the effect of fixed inbreeding fertilisation strategy on increasing selection for inbreeding avoidance through mate choice was weak or nelgigible. A weak effect is discernable in the contrast between Figure 2B and Figure 1B, in which the grand mean inbreeding mating strategy allele value is $-0.627$ when inbreeding fertilisation strategy is not fixed (Figure 1B) versus $-1.036$ when it is fixed (Figure 2B) in generation 10000. Values of $-0.627$ versus $-1.036$ correspond to an outbred focal female being $1.157$ versus $1.260$ times more likely to choose a non-relative than a full sibling as a mate, respectively. Therefore, when females were unable to bias fertilisation to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was not greatly strengthened.

@@

Multiple studies have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].

@@

>>>>

Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of inbreeding fertilisation strategy facilitates selection for polyandry, shows evolution of tendency for polyandry and inbreeding mating strategy when inbreeding fertilisation strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle. In all cost combinations of Figure 2 (panels A-D), tendency for polyandry allele values decreased over generations, reflecting evolution of monandry. However, values of inbreeding mating strategy alleles did not greatly differ over generations when inbreeding fertilisation strategy was fixed, meaning that the effect of fixed inbreeding fertilisation strategy on increasing selection for inbreeding avoidance through mate choice was weak or nelgigible. A weak effect is discernable in the contrast between Figure 2B and Figure 1B, in which the grand mean inbreeding mating strategy allele value is $-0.627$ when inbreeding fertilisation strategy is not fixed (Figure 1B) versus $-1.036$ when it is fixed (Figure 2B) in generation 10000. Because females have 20 alleles with additive effects on inbreeding mating strategy, an average female is therefore expected to have mean inbreeding mating strategy phenotype values of $M_{p} = -0.627 \times 20 = -12.54$ and $M_{p} = -1.036 \times 20 = -20.72$ for not fixed versus fixed inbreeding fertilisation strategy, respectively. These values would cause an outbred focal female to be $2.135$ and $4.180$ times more likely to choose a non-relative than a full sibling as a mate given not fixed fersus fixed inbreeding fertilisation strategy, respectively. Therefore, when females were unable to bias fertilisation to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was strengthened.

@@

@@

<!---  Concluding paragraph below --->

Studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009]. Other studies have

However, empirical hypothesis testing typically does not attempt to predict *a priori* whether or not inbreeding avoidance will be enacted before or after copulation, or if both pre-copulatory and post-copulatory inbreeding avoidance will evolve. Here we have shown that evolution of inbreeding strategies and associated polyandry are predicted to affected by direct costs, and constraints and adaptations of

<!---     ----------------------------------------------------------------     --->
